Executive Constraints and Civil Conflict Onset

### 2020-02-27 paper.Rmd
Move sim summary to rmarkdown and remove old R scripts

```{r eval = F, warning = F}
load("posteriors/sim/simulated_summary.RData")

@@

```{r eval = F, warning = F}
latent.df <- arrange(latent.df, true_value) %>%
    mutate(idx = 1:n())

ggplot(latent.df, aes(idx, true_value)) +
    geom_point(col = "darkgrey") +
    geom_errorbar(aes(ymin = codelow, ymax = codehigh), alpha = 0.2, col = "darkblue") +
    ylab("True Value") +
    theme(axis.text.x = element_blank(),
          axis.title.x = element_blank(),
          axis.ticks.x = element_blank())

```{r eval = F, results = 'hide'}
x <- with(latent.df, mean(true_value <= codehigh & true_value >= codelow))
#x * 100

#plot(df$lg_se[, 1], df$lg[, 1] - colMeans(lg_est))
#plot(df$lg_se[, 1], lapply(lg_est, IQR) %>% unlist)

#which(df$lg[, 1] + 2 * df$lg_se[, 1] < colMeans(lg_est) |
#      df$lg[, 1] - 2 * df$lg_se[, 1] > colMeans(lg_est))

#v <- lapply(theta_old, IQR) %>% unlist
#plot(df$lg_se[, 1], v[df$obs_idx])

#plot(density(p), xlim = c(0, 1), ylim = c(0, 2))
#for (i in 1:100) lines(density(p_hat[i, ]), col = alpha("lightblue", 0.2))

#table(colMeans(p_hat) > .5, y)

>>>>

```{r eval = F, warning = F}
true_values <- readRDS("posteriors/sim/simulated_parameters.rds")

fa <- read_post("posteriors/sim/fa_posteriors.csv")
reg <- read_post("posteriors/sim/reg_posteriors.csv")

fit <- bind_cols(fa, reg)

post <- post_summarise(fit, c("lambda", "psi", "gamma", "delta",
                              "kappa", "rho", "eta", "alpha", "beta",
                              "sigma")) %>%
    rename(codelow = `2.5%`, median = `50%`, codehigh = `97.5%`) %>%
    mutate(type = "Posterior Estimate")

pars.df <- filter(true_values, !grepl("theta", parameter)) %>%
    bind_rows(post) %>%
    mutate(type = as.factor(type))

@@

```{r eval = F, warning = F}
latent.df <- post_summarise(fit, pars = "theta", probs = c(0.025, 0.975)) %>%
    rename(codelow = `2.5%`, codehigh = `97.5`)

x <- mean(theta <= latent.df$codehigh & theta >= latent.df$codelow)
